---
title: "Quickstart guide to initializing a Hackathon"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{quickstart}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Hackathon)
```

# Initialize private repo

```{r}
h = setup_hack('.', 'Example-Hackathon', name = 'Example', desc = 'Predicting iris species')
```

# Collect data

Good hackathon data:
  1.  Can't be easily googled,
  2.  Is from a real-world scientific or business problem,
  3.  Contains enough observations that sufficient data can be held-out for model scoring,
  4.  Contains enough signal that it's not hopeless,
  5.  But not so much signal that it's trivial.
  
Note that often items 2, 3 and 4 are in conflict with each other!

```{r}
data(iris)
```

## Split public / private data


## Check that there is at least some predictive skill



# Initialize public repo

## Load and update team manifests

Needs a `contestant` field. Url is generated from gh_handle in this case.
```{r}
sheet = googlesheets4::read_sheet('sheet')  %>% dplyr::rename(contestant = `Display pseudonym for rankings`, gh_handle = `Your github handle`)
```

Write manifest to version-controlled file (could be made optional?)
The file ultimately needs a `contestant` and `prediction_url` field.
```{r}
update_gs_manifest(sheet, hack = h)
```

Returns `TRUE` or with warnings.

## Score
```{r}
truth = readRDS('private/test_LABELS.rds') %>% as.data.frame()
h = load_hack('.', truth = truth)
```